### 2018-03-29 latex/sc18/experiments.tex
Note on scaling up to 512 nodes
software environment details

\subsection{Machine Details}
The entire experimentation was performed on Eos, a supercomputer at the Oak Ridge Leadership Computing Facility. 
Eos is a 736-node Cray XC30 cluster of Intel Xeon E5-2670 processors with a total of 47.104TB of memory. 
Its compute nodes are organized in blades where each blade contains 4 nodes, and every node has 2 sockets with 8 physical cores and 64GB memory. 
The machine support Intel's hyper-threading (HT), but we restricted it because HT offers minimal improvement for BLAS and LAPACK operations. 
In total, the Eos compute partition contains 11,776 traditional processor cores and our experiments used up to 4,096 cores (35\% of the machine).
\grey{add compiler and blas details}

>>>>

\subsection{Machine Details}
The entire experimentation was performed on Eos, a supercomputer at the Oak Ridge Leadership Computing Facility. 
Eos is a 736-node Cray XC30 cluster of Intel Xeon E5-2670 processors with a total of 47.104TB of memory. 
Its compute nodes are organized in blades where each blade contains 4 nodes, and every node has 2 sockets with 8 physical cores and 64GB memory. 
The machine support Intel's hyper-threading (HT), but we restricted it because HT offers minimal improvement for BLAS and LAPACK operations. 
In total, the Eos compute partition contains 11,776 traditional processor cores and our experiments used up to 4,096 cores (35\% of the machine).

Our objective of the implementation is using open source software as much as possible 
to promote reproducibility and reuse of our code.
Unlike Liavas \cite{LK+17b} that uses Eigen matrix library, we use Armadillo \cite{sanderson2010} for matrix representation
and operations.  
In Armadillo, the elements of the dense matrix are stored in column major order.
For dense BLAS and LAPACK operations, we linked Armadillo with the default LAPACK/BLAS wrappers from Cray. 
For compiler, we use GNU C++ Compiler (g++ (GCC) 6.3.0) and MPI library is from Cray.  We could also 
compile and run the code in RHEA the commodity cluster from OLCF with entire open source libraries such as OpenBLAS and OpenMPI.

\grey{add compiler and blas details}
